---
title: "Summary Report of Sales for Parviflora Stores"
subtitle: "Data was gathered from system generated files for input period"
date: "Generated: `r format(Sys.time(), '%d %B, %Y')` "
output: 
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}

daff <- read_rds("data/processed/integrated_data.rds")
source(list.files(pattern = "4_analysis*.R$", recursive = TRUE))
# get header used later
p <- get_period_header(daff)
```

## Stores Analysis
##
#### Top 3 Stores in terms of revenue `r p` were: 

``` {r top_revenue_stores_text, echo=FALSE}
daff %>% select(store_name, month, rev_total) %>% group_by(store_name) %>% summarise(`Total Revenue` = sum(rev_total)) %>% arrange(desc(`Total Revenue`)) %>% head(3)

```

```{r top_revenue_stores_bar1, fig.show="hold", out.width="50%", echo=FALSE}

plot1 <- horizontal_bar_stores(daff, period = p, save=FALSE)
plot2 <- horizontal_bar_stores_counts(daff, p, save = FALSE)
plot(plot1)
plot(plot2)

```
### Store performance relative to mean
The horizontal axis indicates how many standard deviations from the mean is the store's revenue

```{r norm_rev_stores, echo=FALSE}
diverging_bar_stores(daff, save=FALSE)
```

### Monthly revenues of Parviflora
``` {r monthly_rev_total, echo= FALSE}
plot3 <- Kuba_plot(daff, save = FALSE)
plot(plot3)
```

### How many flowers of each type sells in particular store
``` {r flower_count_per_store, echo = FALSE}

```

### What is the revenue per order for each flower type
```{r bar_order, echo=FALSE}
bar_order_flower(daff, save=FALSE)
```

```{r separate flower counts, fig.show="hold", out.width="50%", echo=FALSE}
sep_flow_count(daff, save=FALSE)
```

#### Stores without the number in sales system for other flowers: 
```{r missing, echo=FALSE}
# TODO Stores that didn't provide us with data in Total Sales Summary
# e.g. store_id 345 doesn't exist in Stores data we need to flag those
# dla Swiebodzina brak danych wszędzie

df_analysis_no_number <- daff[rowSums(is.na(daff)) > 0, ]
df_analysis_no_number %>%
  select(store_name, store_number) %>%
  distinct(store_name, store_number)
```

TODO:
1. Colors per flower mapping 
2. Bar chart - flowers count per store - use: df_flower_analysis
3. Scatter plot count vs. revenue (flower color)
4. 


