---
title: "Summary Report of Sales for Parviflora Stores"
subtitle: "Data was gathered from system generated files for input period"
date: "Generated: `r format(Sys.time(), '%d %B, %Y')` "
output: 
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}

daff <- read_rds("data/processed/integrated_data.rds")
flower_analysis <- read_rds("data/processed/tidy_data.rds")
source(list.files(pattern = "4_analysis*.R$", recursive = TRUE))
# get header used later
p <- get_period_header(daff)
```

## Data Overview

```{r overview, echo=FALSE}
print("Totals summary for Jan")
daff %>%
  filter(month == 1) %>%
  select(count_total, rev_total) %>%
  summary()
print("Totals summary for Feb")
daff %>%
  filter(month == 2) %>%
  select(count_total, rev_total) %>%
  summary()
print("Totals summary for March")
daff %>%
  filter(month == 3) %>%
  select(count_total, rev_total) %>%
  summary() %>%

```


## Stores Analysis
##
#### Top 3 Stores in terms of revenue `r p` were: 

``` {r top_revenue_stores_text, echo=FALSE}
daff %>% select(store_name, month, rev_total) %>% group_by(store_name) %>% summarise(`Total Revenue` = sum(rev_total)) %>% arrange(desc(`Total Revenue`)) %>% head(3)

```

```{r top_revenue_stores_bar11, fig.show="hold", out.width="50%", echo=FALSE}

horizontal_bar_stores(daff, period = p, save=FALSE)
horizontal_bar_stores_counts(daff, p, save = FALSE)

```

### Store performance relative to mean
The horizontal axis indicates how many standard deviations from the mean is the store's revenue

```{r norm_rev_stores, echo=FALSE}
diverging_bar_stores(daff, save=FALSE)
```

### Flower composition varies between the stores
``` {r flower_composition, echo= FALSE}
flower_composition(flower_analysis, p, save = FALSE)

```

```{r top_revenue_stores_bar1, fig.show="hold", out.width="50%", echo=FALSE}
bar_tot_flower(flower_analysis, p, what = "rev", save = FALSE)
bar_tot_flower(flower_analysis, p, what = "count", save = FALSE)
```

### Monthly revenues of Parviflora
``` {r monthly_rev_total, echo= FALSE}
plot3 <- Kuba_plot(daff, save = FALSE)
plot(plot3)
```

### 
``` {r adsa, fig.show="hold", out.width="50%", echo = FALSE}
bar_flower_month(flower_analysis, p, daf = TRUE, save = FALSE)
sep_flow_count(flower_analysis, p, save = FALSE)
```

### What is the revenue per order for each flower type
```{r bar_order, echo=FALSE}
bar_order_flower(flower_analysis, save=FALSE)
scatter_count_rev(flower_analysis, p, save=FALSE)
hist_mean_order(flower_analysis, save=FALSE)
```


#### Stores without the number in sales system for other flowers: 
```{r missing, echo=FALSE}
# TODO Stores that didn't provide us with data in Total Sales Summary
# e.g. store_id 345 doesn't exist in Stores data we need to flag those
# dla Swiebodzina brak danych wszędzie

df_analysis_no_number <- daff[rowSums(is.na(daff)) > 0, ]
df_analysis_no_number %>%
  select(store_name, store_number) %>%
  distinct(store_name, store_number)
```

